MLISA: Machine Learning-based \\ Intelligent Service Agents (to change)

### 2014-09-14 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

@@

\subsubsection{filtered data}\label{sss:filtereddata}
We have adopted the web service data set provided by \cite{10.1109/ISSRE.2011.17}. The raw data provides real-world QoS evaluation results from several users on 5,825 Web services over 64 different time frames\footnote{http://www.wsdream.net/}. In this data set, each web service is associated with a number of features that reflect its functionality. By summarizing the data provided for each web service over different time slots, we have acquired three quality feature for each individual web service. There quality features are the three internal features introduced in section \ref{s:if}: \emph{throughput}, \emph{availability} and \emph{execution time}. 
%To engage in communities, we add two additional external features that reflect web services estimation of its quality metrics compared to other web services. 
Therefore, we have generated an array of web services with 3 distinct features.

Now we want to setup a set of feature vectors representing the communities of web services, for our training purposes. For communities we add two additional external features as discussed in section \ref{s:ef} that reflect the community's estimation of its quality metrics compared to other web services.

\subsubsection{feature engineering}\label{sss:feng}
\subsubsection{feature vector generation}\label{sss:fvg}

>>>>

line1

@@

\subsubsection{filtered data}\label{sss:filtereddata}

We have adopted the web service data set provided by \cite{10.1109/ISSRE.2011.17}. The raw data provides real-world QoS evaluation results from several users on 5,825 Web services over 64 different time frames\footnote{http://www.wsdream.net/}. In this data set, each web service is associated with a number of features that reflect its functionality. By summarizing the data provided for each web service over different time slots, we have acquired three quality feature for each individual web service. There quality features are the three internal features introduced in section \ref{s:if}: \emph{throughput}, \emph{availability} and \emph{execution time}. 
%To engage in communities, we add two additional external features that reflect web services estimation of its quality metrics compared to other web services. 
Therefore, we have generated an array of web services with 3 distinct features.

Now we want to generate a set of feature vectors representing the communities of web services, for our training purposes. For communities we add two additional external features as discussed in section \ref{s:ef} that reflect the community's estimation of its quality metrics compared to other web services. Therefore we formulate a \emph{Community Feature Vector (CFV)} as $CFV_{<C>} = \{f_1,...f_5\}$ having community of $k$ web services. $C = {ws_1,...ws_k}$. The features $f_1$ through $f_5$ represent the \emph{execution time}, \emph{throughput}, \emph{availability}, the \emph{external parameter 1 and 2} correspondingly. A set of communities, with their feature vectors and utilities evaluated provides our algorithm with raw training data set. We call this set the \emph{Community Set (CS)}.

%\subsubsection{feature engineering}\label{sss:feng}
\subsubsection{feature vector generation}\label{sss:fvg}
